GVN-Hoist: Hoisting Computations from Branches

### 2016-08-11 hoist.tex
formalisation of partition algorithm

\begin{verbatim}
BasicBlock B1, B2, B3 // B1 != B2 != B3
DFSIn(B1) = depth first discovery time stamp
DFSIn(B1,B2) = abs(DFSIn(B1) - DFSIn(B2))
DFSIn(B1,B3) = abs(DFSIn(B1) - DFSIn(B3))
BBDist(B1,B2) = BBDist(B1, nearest-common-dom(B1, B2))
BBDist(B1,B3) = BBDist(B1, nearest-common-dom(B1, B3))

@@

Same property would hold for instructions I1, I2, I3 provided they are not fully
redundant i.e., none of the basic blocks containing I1, I2 and I3 dominate the
other.

\begin{verbatim}
DFSIn(I1) = DFSIn of containing basic block
DFSIn(I1,I2) = abs(DFSIn(I1) - DFSIn(I2))
DFSIn(I1,I3) = abs(DFSIn(I1) - DFSIn(I3))
BBDist(I1,I2) = BBDist(I1, nearest-common-dom(I1, I2))
BBDist(I1,I3) = BBDist(I1, nearest-common-dom(I1, I3))

>>>>

\begin{verbatim}
BasicBlock B1, B2, B3 // B1 != B2 != B3
DFSIn(B1) = depth first discovery time stamp
DFSIn(B1,B2) = |DFSIn(B1) - DFSIn(B2)|
DFSIn(B1,B3) = |DFSIn(B1) - DFSIn(B3)|

Depth(B1) = depth of tree from the root node.
// When B1 dominates B2
BBDist(B1, B2) = |Depth(B1) - Depth(B2)|

NCD(B1, B2) = nearest common dominator of B1 and B2
BBDist(B1,B2) = BBDist(B1, NCD(B1, B2))
BBDist(B1,B3) = BBDist(B1, NCD(B1, B3))

@@

Same property would hold for instructions I1, I2, I3 provided they are not fully
redundant i.e., none of the basic blocks containing I1, I2 and I3 respectively
dominate the other:

\begin{verbatim}
Instruction I1, I2, I3
// I1, I2, I3 are not fully redundant
// B1, B2, B3 contains I1, I2, I3 respectively
DFSIn(I1) = DFSIn(B1)
BBDist(I1, I2) = BBDist(B1, B2)
DFSIn(I1) = DFSIn(B1)
DFSIn(I1,I3) = DFSIn(B1, B3)
NCD(I1, I2) = NCD(B1, B2)
